Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-14 trunk/constantRate/ConstCompFuzzExt.tex
Added notes on problems with the proof

\title{Constant Error Tolerance Computational Fuzzy Extractors}
\author{Ran Canetti \and Benjamin Fuller\footnote{The work of B. Fuller is sponsored by Assistant Secretary of Defense for Research \& Engineering under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p, seed)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$ set $c_i' = 0$.
\subitem Else set $c_i' = 1$.
\item Set $c = \decode$.
\item Output $c$.
\end{enumerate}
\vspace{0.45in}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

%\begin{lemma}
%\label{lem:code bits statistically indist}
%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.  Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
%\end{lemma}
%\begin{proof}
%\bnote{Do this}
%\end{proof}
%We can extend this lemma to the entire codeword $C$:
%\begin{lemma}
%For all $c_1, c_2 \in C$ we have the following: 
%\[
%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
%\]
%\end{lemma}
The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
\bnote{As stated above I don't think this proof is right?}
\begin{lemma}
Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$
\end{lemma}
\begin{proof}
Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).  For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$. 
\begin{align*}
\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\
\end{align*}
If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.
\end{proof}
\begin{corollary}
\label{cor:avg min after view}
$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
\end{corollary}
\begin{proof}
Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
Taking the negative log of the above lemma one has:
\begin{align}
\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
 &=\\-\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\\
&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right)\\
%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\\
&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \\
&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
&= |C| - |\mathcal{I}^c| -\ngl(n)\label{eq:min ent}
\end{align}
\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}
Here the Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
\end{proof}

%\begin{lemma}
%\label{lem:obf has hill ent}
%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{proof}
%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.  Let $ (X, Y)  = (C, 
%\end{proof}
%By similar reasoning we can extend this lemma to the entire codeword:
%\begin{lemma}
%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{lemma}
%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
%\end{lemma}

>>>>

\title{Constant Error Tolerance Computational Fuzzy Extractors}
\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
work was sponsored by the Department of the Air Force under Air Force
Contract
\#FA8721-05-C-0002.  Opinions,
interpretations, conclusions and recommendations are those of the author
and
are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$ set $c_i' = 0$.
\subitem Else set $c_i' = 1$.
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

%\begin{lemma}
%\label{lem:code bits statistically indist}
%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.  Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
%\end{lemma}
%\begin{proof}
%\bnote{Do this}
%\end{proof}
%We can extend this lemma to the entire codeword $C$:
%\begin{lemma}
%For all $c_1, c_2 \in C$ we have the following: 
%\[
%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
%\]
%\end{lemma}
The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
\bnote{As stated above I don't think this proof is right?}
Let $c\in C|C_{\mathcal{I}^c}$, then $\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+\ngl(n)$
Let $c\in C|C_{\mathcal{I}^c}$.  Let $P_c =\Pr[C=c | C_{\mathcal{I}^c}]$.  
%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$).  For $b\in\{0,1\}$, by \lemref{lem:code bits statistically indist}, we have that in expectation each for each $i$, $\Pr[C_i =1 ] = 1/2$. 
\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c | C_{\mathcal{I}^c} \wedge view ] &\leq \Pr[C=c | C_{\mathcal{I}^c} ]+ \ngl(n) = P_c+\ngl(n)\\
If this was not true~(that is in expectation, the probability of $c$ increased by a polynomial factor, then the statistical distance between $c$ and some other codeword $c'$ would be $1/\poly(n)$ violating \lemref{lem:codewords in I close}.
\begin{corollary}
\label{cor:avg min after view}
$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq  \Hav(C | C_{\mathcal{I}^c}) - \ngl(n) = |C| - |\mathcal{I}^c| - \ngl(n)$.
\end{corollary}
Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
Taking the negative log of the above lemma one has:
\begin{align}
\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
 &=\nonumber \\
 -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (P_c + \ngl(n))\nonumber \\
&\geq -\log(P_c+ \frac{1}{n^{e}} )= -\log \left(\frac{n^{e}+P_c}{P_c n^{e}}\right) \nonumber \\
%&=-\left(\log (n^w+2) -\log 2 -\log n^w \right)\\
&=-\log P_c-\left(\log (1+\frac{P_c}{n^e}) \right)\nonumber \\
&\geq \Hav(C | C_{\mathcal{I}^c})-\frac{1}{\ln 2}\left(\ln (1+\frac{1}{n^e}) \right) \nonumber \\
&= \Hav(C | C_{\mathcal{I}^c})- \frac{1}{\ln 2}\left(\sum_{i=1}^\infty \frac{(-1)^{i+1}}{i} (\frac{1}{n^e})^i\right) \label{eq:taylor approx} \\
&\geq \Hav(C | C_{\mathcal{I}^c}) - \frac{1}{\ln 2} \frac{1}{n^e} = \Hav(C | C_{\mathcal{I}^c})-\ngl(n) \label{eq:taylor trunc}\\
&= |C| - |\mathcal{I}^c| -\ngl(n) \label{eq:min ent}
\end{align}
\bnote{I think the right thing to say here is that the entropy is $\geq \max\{ |C|, O(1)\}$ since the $\ngl$ term probably dominates the above.}Equation~\ref{eq:taylor approx} is derived using the Taylor expansion for $\ln(1+x)$, Equation~\ref{eq:taylor trunc} is derived by noting it is a geometric series and thus all terms $i=3,....$ are contained in the second term $i=2$ which is positive, and Equation~\ref{eq:min ent} is derived using \clref{cl:many locations ent}.
%\begin{lemma}
%\label{lem:obf has hill ent}
%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{proof}
%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.  Let $ (X, Y)  = (C, 
%\end{proof}
%By similar reasoning we can extend this lemma to the entire codeword:
%\begin{lemma}
%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{lemma}
%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
%\end{lemma}
